\section{Expert assessment}

\subsection{Process }\label{sec:process-}
\subsubsection{Assessment process}

\bigskip
The openETCS documents from the development process should be made available to the assessor. All documents should be submitted and need to be reviewed for content and form by the assessor as well as reflected and evaluated in the project life cycle and CENELEC standard EN 50128:2011. The results should continually be relayed to the responsible entities within the project Work Packages. Due to the agile workflow in the openETCS project this assessment process should be done iteratively.
\bigskip

\subsubsection{Review of Planning Documents}
The planning documents for quality assurance (software quality assurance plan, software verification plan, software validation plan, software coding standards, software configuration management plan and software maintenance plan) will be reviewed for changes. Also the deliverables will be reviewed for plausibility and compliance with standards.
\bigskip


\bigskip
\subsubsection{Initial Assessment }

As it is stated in the D4.5.1 “Assessment Plan” the assessment process in the openETCS project is performed in an agile way. Following agreed on milestones are listed:

\begin{itemize}	
\item  December 2013 1st assessment
\item  February 2014 1st assessment synchronization meeting Nürnberg
\item  Freeze on project development process assessment related inputs for the assessment: 30.09.2015
\item  Release of Assessment Report part related to project development process assessment related as review: 16.10.2015
\item Freeze on toolchain related inputs for the assessment: 17.10.2015
\item  Release of Assessment Report part related to toolchain as review: 30.10.2015
\item Freeze on documents for assessment: 15.11.2015
\item  Release of Assessment Report as review: 4.12.2015
\end{itemize}


\subsection{Sections assessed}\label{sec:sections-assessed}
The sections of the EN 50128:2011 standard which have been applied for the assessment process on the project are listed in following table.



\tablefirsthead{
	\hline 
	\rowcolor{gray} 
	SECTION TO BE ASSESSED & Section & Was assessed \\\hline}
\begin{supertabular}{| m{6cm} | m{2cm} | m{2cm} |}
	Goals, conformity and software safety integrity level & 4 & yes\\\hline


	 
\end{supertabular} 

\FIXME{\%finishing table from Word document section 4.2}
\bigskip
\bigskip